---
title: "Powers Package Vignette"
author: "Hayden Scheiber"
date: "`r Sys.Date()`"
output: rmarkdown::pdf_document
r_check_args: "--no-build-vignettes"
vignette: >
  %\VignetteIndexEntry{Powers Package Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(powers)
```

The `powers` package is an R package with a few functions that can be used as an alternative to the `^` or `**` operators.

Below are some example usages of the functions found in this package.

You can easily square or cube numerical data.
```{r}
square(2)
cube(3.5)
reciprocal(0.5)
```

The functions in this package can also be used to take vectors of numbers to powers.
```{r}
square(1:10)
cube(1:10)
reciprocal(1:10)
```

The functions also work on logical data, coercing it to numerical data.
```{r}
square(TRUE)
cube(FALSE)
reciprocal(FALSE)
```

You might be wondering why anyone would use these functions over the basic `^` function. These functions also have a plotting capability!
Using the switch `plot_it = TRUE` any of the `powers` functions can be made to output a plot of the input vector vs its power (different for every function).
You can also output the plot as an object using `returnPlot = TRUE`. The last input, `returnVal = FALSE` allows you to supress the raw output of numbers or characters.

For example:
```{r}
my_plot <- square(1:20, plot_it = TRUE, returnVal = FALSE, returnPlot = TRUE)
```


To make a plot of any arbitrary power, use the `pwr` function:
For example, taking the 5th power:
```{r}
my_plot2 <- pwr(1:20, a = 5, plot_it = TRUE, returnVal = FALSE, returnPlot = TRUE)
```

The `powers` functions also work on character data! These functions generall works as follows:

- Taking the positive power of some string ouputs that string repeated a number of times equivalent to the absolute value of the exponent, separated by spaces in the output. For example:
```{r}
pwr("This text should repeat thrice.", a = 3)
```

- Taking the zeroth power of a string outputs only the first character of that string. For example:
```{r}
pwr("The output of this should be T", a = 0)
```

- Taking negative powers of a string will first reverse the order of the input string, and then repeat this reversed string. For example:
```{r}
pwr("Hello World", a = -3)
```

That's all there is to it really! I hope this vignette has been informative for you. The library is completely free to use by anyone, just include the license when exporting. Cheers!
